Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-10 paper/disc20clustering.tex
OPT undefined
Comments

@@

@@

First, we construct a ground set of size $k-1$ on an arbitrary cluster $S$.
In any configuration, there exists an isolated node on $S$.
We issue requests between the current isolated node from $S$, and some node that was initially collocated with it.
Repeating such requests, almost all the nodes must visit the cluster $S$.
In comparison, \OPT performs only two migrations.

>>>>

\maciek{Above definition is the definition of strict competitive ratio. In comparison to non-strict with additive constant. Emphasize? Maybe already use the notion of \OPT}

@@

\maciek{emphasize that all our algorithms have strict competitive ratio}

@@

First, we construct a ground set of size $k-1$ on an arbitrary cluster $S$.
In any configuration, there exists an isolated node on $S$.
We issue requests between the current isolated node from $S$, and some node that was initially collocated with it.
Repeating such requests, almost all the nodes must visit the cluster $S$.
In comparison, we show that there exists an optimal offline algorithm \OPT that performs only two migrations.
